Data analysis to support temporary cycleways

### 2020-05-06 README.Rmd

# London

```{r}
## Mask not required for London, so no need to slow down the code unnecessarily
# london_centroids = get_pct_centroids("london",geography = "lsoa") %>% sf::st_transform(27700)
# london_lsoa_buff = st_buffer(x = london_centroids, dist = 1000)
# london_res_buff = st_intersection(builtup,london_lsoa_buff) %>% st_union()
s = c(
  "Esri.WorldGrayCanvas",
  "https://b.tile-cyclosm.openstreetmap.fr/cyclosm/{z}/{x}/{y}.png",
  "https://server.arcgisonline.com/ArcGIS/rest/services/World_Imagery/MapServer/tile/{z}/{y}/{x}'"
)
region = las_top %>% filter(name == "London")
roads = rsf %>% filter(region == "London", pctgov > 500)
# roads = roads %>% st_transform(27700) %>% st_intersection(london_res_buff) %>% st_transform(4326)

roads_top = roads %>%
  filter(length > 500) %>%
  filter(!name == "Talgarth Road", length > 500) %>%
  filter(!name == "Whitechapel Road", length > 500) %>%
  arrange(desc(pctgov)) %>%
  slice(1:10)
# tm_shape(roads_top) + tm_lines("pctgov", lwd = 3, palette = "viridis") +
#   tm_text("name") +
#   tm_view(set.view = 12) + tm_scale_bar()
tm_shape(roads) + tm_lines("lightblue", lwd = 3, alpha = 0.7) +
  tm_shape(roads_top) + tm_lines(col = "blue", lwd = 3) +
  tm_text("name") +
  tm_view(set.view = 12) +
  tm_scale_bar() +
  tm_basemap(server = s)
roads_top %>%
  st_drop_geometry() %>%
  select(name, ref, road_type = highway, cycling_potential = pctgov, length_m = length) %>%
  knitr::kable(digits = 0)
```

# Birmingham

```{r}
# idea: use buffers of LSOA centroids to supplent built-up areas
# birmingham_centroids = get_pct_centroids("west-midlands", geography = "lsoa")
# birmingham_lsoa_buff = stplanr::geo_buffer(birmingham_centroids, dist = 1000)
# mapview::mapview(birmingham_lsoa_buff)
# birmingham_res_buff = st_intersection(builtup, birmingham_lsoa_buff) %>% st_union()
# roads = roads %>%
#   st_transform(27700) %>%
#   st_intersection(birmingham_res_buff) %>%
#   st_transform(4326)
# idea: look for other basemaps
region = las_top %>% filter(name == "Birmingham")
roads = rsf %>% filter(region == "Birmingham", pctgov > 100)
roads = st_intersection(roads, region) # remove roads outside region

roads_top = roads %>%
  filter(length > 300) %>%
  arrange(desc(pctgov)) %>%
  slice(1:10)
tm_shape(roads) + tm_lines("lightblue", lwd = 3, alpha = 0.7) +
  tm_shape(roads_top) + tm_lines(col = "blue", lwd = 3) +
  tm_text("name") +
  tm_view(set.view = 12) + tm_scale_bar() +
  tm_basemap(server = s)

roads_top %>%
  st_drop_geometry() %>%
  select(name, ref, road_type = highway, cycling_potential = pctgov, length_m = length) %>%
  knitr::kable(digits = 0)
```

# Manchester

```{r}
roads = rsf %>% filter(region == "Manchester", pctgov > 100)
region_centre = tmaptools::geocode_OSM("Manchester", as.sf = TRUE)
region_buff = stplanr::geo_buffer(region_centre, dist = 7000)
roads = st_intersection(roads, region_buff)

roads_top = roads %>%
  filter(length > 300) %>%
  arrange(desc(pctgov)) %>%
  slice(1:10)
tm_shape(roads) + tm_lines("lightblue", lwd = 3, alpha = 0.7) +
  tm_shape(roads_top) + tm_lines(col = "blue", lwd = 3) +
  tm_text("name") +
  tm_view(set.view = 12) + tm_scale_bar() +
  tm_basemap(server = s)
roads_top %>%
  st_drop_geometry() %>%
  select(name, ref, road_type = highway, cycling_potential = pctgov, length_m = length) %>%
  knitr::kable(digits = 0)
```

# Leeds

```{r}
leeds_centre = tmaptools::geocode_OSM("Leeds", as.sf = TRUE)
leeds_buff = stplanr::geo_buffer(leeds_centre, dist = 4000)
roads = rsf %>% filter(region == "Leeds", pctgov > 100)
region_centre = tmaptools::geocode_OSM("Leeds", as.sf = TRUE)
region_buff = stplanr::geo_buffer(region_centre, dist = 9000)
roads = st_intersection(roads, region_buff)

roads_top = roads[leeds_buff, ] %>%
  filter(length > 300) %>%
  filter(name != "Broadway") %>%
  filter(name != "Wellington Street") %>%
  arrange(desc(pctgov)) %>%
  slice(1:10)
tm_shape(roads) + tm_lines("lightblue", lwd = 3, alpha = 0.7) +
  tm_shape(roads_top) + tm_lines(col = "blue", lwd = 3) +
  tm_text("name") +
  tm_view(set.view = c(-1.549, 53.805, 13)) + 
  tm_scale_bar() +
  tm_basemap(server = s)

roads_top %>%
  st_drop_geometry() %>%
  select(name, ref, road_type = highway, cycling_potential = pctgov, length_m = length) %>%
  knitr::kable(digits = 0)
```

# Liverpool

```{r}
roads = rsf %>% filter(region == "Liverpool", pctgov > 100)
region = las_top %>% filter(name == "Liverpool")
roads = st_intersection(roads, region)
# region_centre = tmaptools::geocode_OSM("Liverpool", as.sf = TRUE)
# region_buff = stplanr::geo_buffer(region_centre, dist = 9000)
# tm_shape(roads) + tm_lines("pctgov", lwd = 3, palette = "viridis") +
#   tm_view(set.view = 10) + tm_scale_bar() +
#   tm_shape(region) + tm_borders()

roads_top = roads %>%
  filter(length > 200) %>%
  filter(name != "Queensway (Mersey Tunnel)") %>%
  filter(name != "Queensway") %>%
  arrange(desc(pctgov)) %>%
  slice(1:10)
tm_shape(roads) + tm_lines("lightblue", lwd = 3, alpha = 0.7) +
  tm_shape(roads_top) + tm_lines(col = "blue", lwd = 3) +
  tm_text("name") +
  tm_view(set.view = c(-2.95, 53.4084, 13)) + 
  tm_scale_bar() +
  tm_basemap(server = s)

roads_top %>%
  st_drop_geometry() %>%
  select(name, ref, road_type = highway, cycling_potential = pctgov, length_m = length) %>%
  knitr::kable(digits = 0)
```

# Bristol

```{r}
region = las_top %>% filter(name == "Bristol")
region = sf::st_make_valid(region)
roads = rsf %>% filter(region == "Bristol", pctgov > 100)
roads = st_intersection(roads, region)

bristol_centre = tmaptools::geocode_OSM("Bristol", as.sf = TRUE)
bristol_buff = stplanr::geo_buffer(bristol_centre, dist = 1500)
roads_top = roads[bristol_buff, ] %>%
  filter(length > 300) %>%
  filter(name != "Temple Way Underpass") %>%
  filter(!name == "Newfoundland Street", !name == "") %>%
  arrange(desc(pctgov)) %>%
  slice(1:10)

tm_shape(roads) + tm_lines("lightblue", lwd = 3, alpha = 0.7) +
  tm_shape(roads_top) + tm_lines(col = "blue", lwd = 3) +
  tm_text("name") +
  tm_view(set.view = c(-2.5879, 51.454, 13)) + 
  tm_scale_bar() +
  tm_basemap(server = s)

roads_top %>%
  st_drop_geometry() %>%
  select(name, ref, road_type = highway, cycling_potential = pctgov, length_m = length) %>%
  knitr::kable(digits = 0)
```

# Leicester

```{r}
roads = rsf %>% filter(region == "Leicester", pctgov > 100)
region_centre = tmaptools::geocode_OSM("Leicester", as.sf = TRUE)
region_buff = stplanr::geo_buffer(region_centre, dist = 9000)
roads = st_intersection(roads, region_buff)

roads_top = roads %>%
  filter(length > 200) %>%
  arrange(desc(pctgov)) %>%
  slice(1:10)

tm_shape(roads) + tm_lines("lightblue", lwd = 3, alpha = 0.7) +
  tm_shape(roads_top) + tm_lines(col = "blue", lwd = 3) +
  tm_text("name") +
  tm_view(set.view = 12) + tm_scale_bar() +
  tm_basemap(server = s)

roads_top %>%
  st_drop_geometry() %>%
  select(name, ref, road_type = highway, cycling_potential = pctgov, length_m = length) %>%
  knitr::kable(digits = 0)
```

# Sheffield

```{r}
roads = rsf %>% filter(region == "Sheffield", pctgov > 100)
region_centre = tmaptools::geocode_OSM("Sheffield", as.sf = TRUE)
region_buff = stplanr::geo_buffer(region_centre, dist = 9000)
roads = st_intersection(roads, region_buff)

roads_top = roads %>%
  filter(length > 200) %>% 
  filter(!name == "Tinsley Roundabout")  %>%
  filter(!name == "Meadowhead Roundabout")  %>%
  arrange(desc(pctgov)) %>%
  slice(1:10)

tm_shape(roads) + tm_lines("lightblue", lwd = 3, alpha = 0.7) +
  tm_shape(roads_top) + tm_lines(col = "blue", lwd = 3) +
  tm_text("name") +
  tm_view(set.view = 12) + tm_scale_bar() +
  tm_basemap(server = s)

roads_top %>%
  st_drop_geometry() %>%
  select(name, ref, road_type = highway, cycling_potential = pctgov, length_m = length) %>%
  knitr::kable(digits = 0)
```

# Newcastle

```{r}
roads = rsf %>% filter(region == "Newcastle", pctgov > 100)
region_centre = tmaptools::geocode_OSM("Newcastle", as.sf = TRUE)
region_buff = stplanr::geo_buffer(region_centre, dist = 9000)
region = las_top %>% filter(name == "Newcastle")
region = st_intersection(region_buff, region)
roads = st_intersection(roads, region)

roads_top = roads %>%
  filter(length > 250) %>%
  filter(!name == "") %>%
  filter(!name == "Redheugh Bridge")  %>%
  filter(!name == "Derwenthaugh Road", !name == "") %>%
  filter(!name == "East Denton Interchange", !name == "") %>%
  arrange(desc(pctgov)) %>%
  slice(1:10)

tm_shape(roads) + tm_lines("lightblue", lwd = 3, alpha = 0.7) +
  tm_shape(roads_top) + tm_lines(col = "blue", lwd = 3) +
  tm_text("name") +
  tm_view(set.view = 12) + tm_scale_bar() +
  tm_basemap(server = s)
roads_top %>%
  st_drop_geometry() %>%
  select(name, ref, road_type = highway, cycling_potential = pctgov, length_m = length) %>%
  knitr::kable(digits = 0)
```

# Cambridge

```{r}
roads = rsf %>% filter(region == "Cambridge", pctgov > 100)
region_centre = tmaptools::geocode_OSM("Cambridge", as.sf = TRUE)
region_buff = stplanr::geo_buffer(region_centre, dist = 3000)
roads = st_intersection(roads, region_buff)

roads_top = roads %>%
  filter(length > 100) %>%
  filter(name != "") %>%
  filter(!name == "Hills Road")  %>%
  arrange(desc(pctgov)) %>%
  slice(1:10)
tm_shape(roads) + tm_lines("lightblue", lwd = 3, alpha = 0.7) +
  tm_shape(roads_top) + tm_lines(col = "blue", lwd = 3) +
  tm_text("name") +
  tm_view(set.view = 13) + tm_scale_bar() +
  tm_basemap(server = s)

roads_top %>%
  st_drop_geometry() %>%
  select(name, ref, road_type = highway, cycling_potential = pctgov, length_m = length) %>%
  knitr::kable(digits = 0)
```

>>>>

```{r, child="london.Rmd"}

```

See [london.html](https://cyipt.github.io/tempCycleways/london.html) for the interactive version of the map above.

```{r, child="birmingham.Rmd"}

```

See [birmingham.html](https://cyipt.github.io/tempCycleways/birmingham.html) for the interactive version of the map above.

```{r, child="manchester.Rmd"}

```

See [manchester.html](https://cyipt.github.io/tempCycleways/manchester.html) for the interactive version of the map above.

```{r, child="leeds.Rmd"}

```

See [leeds.html](https://cyipt.github.io/tempCycleways/leeds.html) for the interactive version of the map above.

```{r, child="liverpool.Rmd"}

```

See [liverpool.html](https://cyipt.github.io/tempCycleways/liverpool.html) for the interactive version of the map above.

```{r, child="bristol.Rmd"}

```

See [bristol.html](https://cyipt.github.io/tempCycleways/bristol.html) for the interactive version of the map above.

```{r, child="leicester.Rmd"}

```

See [leicester.html](https://cyipt.github.io/tempCycleways/leicester.html) for the interactive version of the map above.

```{r, child="sheffield.Rmd"}

```

See [sheffield.html](https://cyipt.github.io/tempCycleways/sheffield.html) for the interactive version of the map above.

```{r, child="newcastle.Rmd"}

```

See [newcastle.html](https://cyipt.github.io/tempCycleways/newcastle.html) for the interactive version of the map above.

```{r, child="cambridge.Rmd"}

```

See [cambridge.html](https://cyipt.github.io/tempCycleways/cambridge.html) for the interactive version of the map above.

```{r, engine='zsh', eval=FALSE}
# deploy
git clone git@github.com:cyipt/tempCycleways
cd tempCycleways
git checkout --orphan gh-pages
git rm -rf .
git commit --allow-empty -m 'Initial gh-pages commit'
# git push origin gh-pages
# git checkout master
# cp -Rv ../README* . # it's 100 MB!
cp -Rv ../*.html . # it's 100 MB!
git status
ls -hal
mv README.html index.html
firefox index.html
git status
git push origin gh-pages
cd ..
echo '*.html' >> .gitignore
echo 'tempCycleways/' >> .gitignore
pandoc -o README.html README.md
```
